%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Bhaskar Mandal} \\ \vspace{1pt}
    \small +91 9647598624 $|$ \href{mailto:hello@bhaskaraa45.me}{\underline{hello@bhaskaraa45.me}} $|$ 
    \href{https://linkedin.com/in/bhaskaraa45}{\underline{linkedin.com/in/bhaskaraa45}} $|$
    \href{https://github.com/bhaskaraa45}{\underline{github.com/bhaskaraa45}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      {Bachelor of Technology in Materials Science and Metallurgical Engineering}{Oct. 2022 -- Present}
      \resumeSubheading
      {Mozampur HSSB High School}{Malda, India}
      {High School}{Jul. 2020 -- Apr. 2022}
    \resumeSubheading
      {Kaliachak Abasik Mission}{Malda, India}
      {High School}{Jan. 2017 -- Feb. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {App Dev Head at Lambda (Software Development Club)}{May 2024 -- Present}
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Rewrote the IITH Dashboard from a PWA to a Flutter app, resulting in increased overall satisfaction from the student community.}
        \resumeItem{Migrated the cab-sharing website to the new dashboard app, ensuring seamless integration and improved user experience.}
        \resumeItem{Building and maintaining websites for the SciTech clubs.}
        \resumeItem{Leading a team of 25 cores to work on projects.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Core Team}{June 2023 - April 2024}
   %  \resumeItemListStart
   %     \resumeItem
   %       {Worked on implementation of IITH Dashboard frontend side.}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Web Head at E-Cell IITH}{May 2024 -- Present}
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built a portal for a hackathon will be conducted by E-Cell in collaboration with NPCI.}
        \resumeItem{Working on implementation of a new E-Cell website.}
        \resumeItem{Leading a team of 4 managers and working with them.}
    \resumeItemListEnd

    \resumeSubheading
      {Core at Lambda (Software Development Club)}{July 2023 -- April 2024}
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Worked on new implementation of IITH Dashboard frontend and auth part.}
      \resumeItemListEnd

    \resumeSubheading
      {App-Web Team Member at Sunshine (Counselling Cell)}{Jun 2023 -- April 2024}
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built an \href{https://play.google.com/store/apps/details?id=com.sunshine.iith}{\underline{app}} for Sunshine, IITH. Its basically Flutter app which use Dialogflow for ChatBot feature and Firebase for database (RTDB) and auth.}
        \resumeItem{Worked on new implementation of the main \href{https://sunshine.iith.ac.in}{\underline{website}}.}
      \resumeItemListEnd

      \resumeSubheading
      {Frontend Developer at PicaPool}{}
      {Indian Institute of Technology, Hyderabad}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Worked as a frontend developer, and built two apps \href{https://play.google.com/store/apps/details?id=com.picapool&hl=en&gl=IN}{\underline{PicaPool}} and \href{https://play.google.com/store/apps/details?id=com.picapool.partner&hl=en&gl=IN}{\underline{PicaPool Partner}}.}
        \resumeItem{Worked on new implementation of the main \href{https://sunshine.iith.ac.in}{\underline{website}}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{URL Shrink} $|$ \emph{\href{https://github.com/bhaskaraa45/url-shortener}{Source Code}} $|$ \emph{Go/Gin, ReactJs, PostgreSQL}} {}
          \resumeItemListStart
            \resumeItem{A web application designed to shrink large URLs and track the number of clicks on the generated short URLs.}
            \resumeItem{Developed using Go/Gin as backend framework, PostgreSQL as database and ReactJS for frontend.}
            \resumeItem{Cookie-based Google authentication for secure user access. And a subdomain utilization for efficient redirection.}
            
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hackathon Portal} $|$ \emph{\href{https://hackathon.bhaskaraa45.me/}{hackathon.bhaskaraa45.me}} $|$ \emph{Go/Gin, ReactJs, PostgreSQL, Supertokens}} {}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive portal for conducting a hackathon organized by E-Cell, IIT Hyderabad in collaboration with NPCI. The portal features both participant and admin interfaces to facilitate smooth event management.}
            \resumeItem{Utilized Next.js and Tailwind CSS for the frontend development. and Go-Gin framework and PostgreSQL for backend and database respectively.}
            \resumeItem{Implemented secure authentication using Supertokens.}

          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{ChatHub} $|$ \emph{\href{https://github.com/oAndBtech/private_chat}{Source Code}} $|$ \emph{Flutter, Go Lang, FCM, Socket.IO}} {}
          \resumeItemListStart
            \resumeItem{ChatHub is designed to offer secure and efficient communication across multiple platforms.}
            \resumeItem{Used Flutter for frontend, GoLang (gorilla/mux) for backend and PostgreSQL for database. And proper FCM (Firebase Cloud Messaging) implemented for notifications.}
            \resumeItem{Implemented secure authentication using Supertokens.}

          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{TicTacToe} $|$ \emph{\href{https://tictactoe.bhaskaraa45.me/}{tictactoe.bhaskaraa45.me}} $|$\emph{\href{https://github.com/bhaskaraa45/tic-tac-toe}{Source Code}} $|$ \emph{Go/Gin, ReactJs, PostgreSQL}} {}
          \resumeItemListStart
            \resumeItem{Multiplayer(2) tic tac toe online game.}
            \resumeItem{Developed using Go-Gin frameworks as backend with Socket.IO for real time communication and React.JS for frontend.}

          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Code Revision} $|$\emph{\href{https://github.com/bhaskaraa45/CodeRevision-android-app}{Source Code}}  $|$ \emph{Java, XML, Firebase}} {}
          \resumeItemListStart
            \resumeItem{This is an android app, allows users to save, categorize, and revisit problems, along with features to add tried and wishlisted questions for better organization and revision.}
            \resumeItem{Developed using Java and XML for the frontend and used Firebase for auth and database (RTDB).}

          \resumeItemListEnd

          
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Java, Python, C/C++, Dart, SQL (Postgres), JavaScript, Typescript, HTML/CSS} \\
     \textbf{Frameworks}{: Flutter, NextJS, Go-Gin, FastAPI, Node.js, Tailwind CSS} \\
     \textbf{Developer Tools}{: Git/GitHub, Linux, Firebase, Google Cloud Platform, Docker, Microsoft Azure, Vercel, Cloudflare} \\
     \textbf{Libraries}{: React JS, Express JS, NumPy, Matplotlib, Pandas}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
